

```{r setup, include=FALSE, class.source = ".rCode"}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(comment = list(bash = "")) # this is to avoid printing bash output with # in front
# If want to do the same for R, can add comment = NA in the chunk part
library(knitr)
```
```{css, echo=FALSE, eval =T}
pre.python {
background-color: mintcream;
}
pre.r {
background-color: #f0fbff;
}
```
```{css, echo=FALSE, eval=F}
pre {
  max-height: 300px;
  overflow-y: auto;
}
```


## How to write .h5 input to run covRunner.py

Will have different H5I_GROUPS (which names need to match the following ones): <br/>

##### 1. **`phenotypes/`**

1.1. subgroup: *`<pheno_subgroup>/`* (e.g. "data_bcNcovariates") <br/>
  
  - \<pheno_subgroup\> corresponds to 'phenos_version'<br/> (refers to the type of phenotypes to analyse, e.g. phenotypes that went through different type of normalization)
  - passed with `--phenos_v` option (**required**); in code, is stored in `self.phenos_version` <br/>

1.2. datasets: <br/>

  - `['matrix']`;
  - `['col_header']['phenotype_ID']`;
  - `['col_header']['covariatesUsed']`; per each phenotype, the comma-sep string of covariates used - names corresponding to `covariate_ID` in `covariates/` (e.g. "sex,age,Batch", "sex,Batch"...)
  - `['row_header']['sample_ID']`
  
<br/>

##### 2. **`covariates/`**
2.1. subgroup: *`<cov_subgroup>/`* (e.g. "data_bcNcovariates") <br/>
  
  - \<cov_subgroup\> corresponds to 'covs_version' <br/> (similar to pheno_subgroup)
  - passed with `--covs_v` option (**required**, set 'None' if not used); in code, is stored in `self.covs_version` <br/>

2.2. datasets: <br/>

  - `['matrix']`;
  - `['col_header']['covariate_ID']`; e.g. "sex", "age", "Batch"
  - `['row_header']['sample_ID']`

<br/>

##### 3. **`cages/`**
3.1. subgroup: *`<cage_subgroup>/`* (e.g. "all") <br/>
  
  - \<cage_subgroup\> corresponds to 'cage_version' <br/> (for different batches or analysis)
  - passed with `--cage_v` option (**required**); in code, is stored in `self.cage_version` <br/>

3.2. datasets: <br/>

  - `['array']`; 
  - `['sample_ID']`

<br/>

##### 4. **`dam/`**
4.1. subgroup: *`<dam_subgroup>/`* (e.g. "mother_name") <br/>
  
  - \<dam_subgroup\> corresponds to 'dam_version' <br/> (for different batches or analysis)
  - passed with `--dam_v` option (**required**, set 'None' if not used); in code, is stored in `self.dam_version` <br/>

4.2. datasets: <br/>

  - `['array']`; 
  - `['sample_ID']`

<br/>

##### 5. **`GRM/`** or **`GRM_LOCO/`**
5.1. subgroup: *`<GRM_subgroup>/`* (e.g. "Andres_kinship") <br/>
  
  - \<GRM_subgroup\> corresponds to 'GRM_version' <br/>
  - passed with `--grm_v` option (**required**); in code, is stored in `self.GRM_version` <br/>

5.2. datasets: <br/>

  - `['matrix']`; 
  - `['row_header']['sample_ID']`

<br/>

##### 6. **`sex_cov/`**
6.1. subgroup: *`<sex_subgroup>/`* (e.g. "all") <br/>
  
  - \<sex_subgroup\> corresponds to 'sex_version'
  - passed with `--sex_v` option, optional (default is 'None'); in code, is stored in `self.sex_version` <br/>

6.2. datasets: <br/>

  - `['array']`; 
  - `['sample_ID']`

<br/>


##### 7. **`subsets/`** <br/>
7.1. *`<subset_name>`* (e.g. "include") <br/>

  - \<subset_name\> is the name of a specific subset, to handle optional subset of individuals, e.g. excluding singletons
  - passed with `-s` option, optional (default is 'None')
  
7.2 datasets: <br/>  

  - `['<subset_name>']`: contains all sample_id that are part of the subset

<br/><br/>



#### Examples

##### A. input.h5 
In R can look at it using, `h5ls("input.h5")`. NB: in this example there is no group "subsets"
```{r , eval=T, comment = NA, echo=F}
library("rhdf5")
h5ls("~/PRJs/HSmice/output/dataset/HSmice_wPleth_noEpoch_HT_v2.h5", )[c("group", "name", "otype")]
```
<br/>

##### B. Example of running the code

Modelling univariate DGE+IEE+cageEffect (i.e. no IGE but include IEE)
```{bash , eval=F, comment = NA, echo=T}
  python covRunner.py \
        --input HSmice.h5 \
        --phenos_v data_bcNcovariates \
        --covs_v data_bcNcovariates \
        --cage_v all \
        --grm_v Andres_kinship \
        --analysis_type VD \
        --out ./ \
        -p 1 \
        -m uni \
        -e DGE,IEE,cageEffect
```
<br/>     

Modelling bivariate DGE+IGE+cageEffect+maternalEffect
```{bash , eval=F, comment = NA, echo=T}
  python covRunner.py \
        --input HSmice.h5 \
        --phenos_v data_bcNcovariates \
        --covs_v data_bcNcovariates \
        --cage_v all \
        --dam_v mother_name \
        --grm_v Andres_kinship \
        --analysis_type VD \
        --out ./ \
        -p 1 \
        -c combins.csv \
        -m bi \
        -e DGE,IGE,cageEffect,maternalEffect \
```
<br/>       

Modelling sexvariate DGE+IGE+cageEffect, with corr_As1s2 constrained to 1
```{bash , eval=F, comment = NA, echo=T}
  python covRunner.py \
        --input HSmice.h5 \
        --phenos_v data_bcNcovariates \
        --covs_v data_bcNcovariates \
        --cage_v all \
        --grm_v Andres_kinship \
        --sex_v all \
        --analysis_type VD \
        --out ./ \
        -p 1 \
        -m sex \
        -e DGE+IGE+cageEffect  \
        -z corr_As1s2,1
```
